PhotoD: LSST photometric distances out to 100 kpc.

### 2023-11-09 paper/methodology.tex
switched red and blue color to correspond to stellar colors in plot3diagsData.png

\begin{figure*}[ht!]
	\plotone{plot3diagsData.png}
	\caption{The blue dots in the left panel show color-magnitude diagram for 841,000 stars from the SDSS Stripe 82 Standard Star Catalog that have Gaia matches within 0.15 arcsec (after correcting for proper motion using Gaia measurements). A subset	of 415,000 stars with $r < 22$ and $u<22$ are shown as red dots, and 409,000 of those that also have $0.2 < g-i < 3.5$ are shown as cyan dots. Finally, 63,000 stars that have signal-to-noise ratio for Gaia’s parallax measurements of at least 20 are shown as green dots. The same color scheme is used in other two panels. The three yellow lines in the middle panel show stellar locus parametrization used by Green et al. (2014) for three values of metallicity (left to right): $[Fe/H] = -2.0, -1.0, 0.0$. In the right panel, the impact of metallicity on color-color tracks is negligible and all three are indistinguishable from each other. } \label{fig:3dataDiags}
\end{figure*}

>>>>

\begin{figure*}[ht!]
	\plotone{plot3diagsData.png}
	\caption{The red dots in the left panel show color-magnitude diagram for 841,000 stars from the SDSS Stripe 82 Standard Star Catalog that have Gaia matches within 0.15 arcsec (after correcting for proper motion using Gaia measurements). A subset of 415,000 stars with $r < 22$ and $u<22$ are overplotted as blue dots, and 409,000 of those that also have $0.2 < g-i < 3.5$ are overplotted as cyan dots. Finally, 63,000 stars that have signal-to-noise ratio for Gaia’s parallax measurements of at least 20 are shown as green dots. The same color scheme is used in other two panels. The three yellow lines in the middle panel show stellar locus parametrization used by Green et al. (2014) for three values of metallicity (left to right): $[Fe/H] = -2.0, -1.0, 0.0$. In the right panel, the impact of metallicity on color-color tracks is negligible and all three are indistinguishable from each other. } \label{fig:3dataDiags}
\end{figure*}
